A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-29 paper/prab.tex
starting to edit theor-exp
conclusion edit

We presented a general-purpose framework for solving multi-objective
  optimization problems.
Its modular design simplifies the application to simulation-based optimization
  problems for a wide range of problems and allows to exchange the
  optimization algorithm.
In a recent work, we successfully implemented and integrated another
  optimization algorithm, originally presented in~\cite{pesc:11}, into our
  framework.
The flexibility of being able to adapt both ends of the optimization
  process, the forward solver and the optimization algorithm simultaneously
  not only leads to broad applicability but it facilitates the ability to
  tailor the optimization strategy to the optimization problem as well.

%This first study shows that the framework is ready to tackle problems arising
%  in the domain of beam dynamics.
%
%Interestingly, the computation of a good approximation of the Pareto front is
%  already feasible on a small cluster using only a modest number of MPI
%  processes.
%  
%For 1000 generations consisting of 2048 feasible and 8354 infeasible function
%  evaluations (simulations) the optimizer needed $845$ minutes on the
%  \textsc{Felsim} cluster on $16$ processes.
%
%When we double the number of processes to $32$ (\textsc{Felsim} allows a
%  maximum of $64$ processes per job) the runtime improves to $302$ minutes (2048
%  accepted and 5426 infeasible individuals).
%Notice that the runtime can vary due to the random nature of the process.
%Nevertheless we see a reasonable speeduo when using more cores to solve the
%  optimization problem. %and the parallel performance will be further evaluated
%  in a forthcoming publication.
%The number of individuals is the only limiting factor.
In this paper we applied the framework to a beam dynamics problem at the AWA.
Optimization of the 3D beam size and energy spread was accomplished.
A scan of time step and hyper parameters was done to determine computational settings.
Then a full scale physics optimization was performed.
The resulting beam tune can and will be used in future TBA experiments at the AWA.
This problem also took advantage of the frameworks massively parallel capabilities by
running on 2624 processes on Bebop at LCRC.

@@

Outlook, ....

>>>>

A general-purpose framework for solving multi-objective
  optimization problems was presented.
Its modular design simplifies the application to simulation-based optimization
  problems for a wide range of problems and allows to exchange the
  optimization algorithm.
In a recent work, we successfully implemented and integrated another
  optimization algorithm, originally presented in~\cite{pesc:11}, into our
  framework.
The flexibility of being able to adapt both ends of the optimization
  process, the forward solver and the optimization algorithm simultaneously
  not only leads to broad applicability but it facilitates the ability to
  tailor the optimization strategy to the optimization problem as well.

%This first study shows that the framework is ready to tackle problems arising
%  in the domain of beam dynamics.
%
%Interestingly, the computation of a good approximation of the Pareto front is
%  already feasible on a small cluster using only a modest number of MPI
%  processes.
%  
%For 1000 generations consisting of 2048 feasible and 8354 infeasible function
%  evaluations (simulations) the optimizer needed $845$ minutes on the
%  \textsc{Felsim} cluster on $16$ processes.
%
%When we double the number of processes to $32$ (\textsc{Felsim} allows a
%  maximum of $64$ processes per job) the runtime improves to $302$ minutes (2048
%  accepted and 5426 infeasible individuals).
%Notice that the runtime can vary due to the random nature of the process.
%Nevertheless we see a reasonable speeduo when using more cores to solve the
%  optimization problem. %and the parallel performance will be further evaluated
%  in a forthcoming publication.
%The number of individuals is the only limiting factor.
The framework was integrated into OPAL, and used 
to study a beam dynamics problem at the AWA.
A scan of time step and hyper parameters was done to determine computational settings.
Then a full scale physics optimization was performed.
Optimization of the 3D beam size and energy spread was accomplished.
The TBA beam line presented is currently being installed at the AWA.
Once installation is complete, 
the results shown here will guide future experiments at the AWA.
%This problem also took advantage of the frameworks massively parallel capabilities by
%running on 2624 processes on Bebop at LCRC.

@@
